Multisensor Architecture for an Intersection Management System

### 2015-04-10 ch2-mdf_ims.tex
Added Kamijo1999 and Kamijo2000 to Bibliography

Intersection monitoring is a required task to be done within intelligent transportation systems for high-level applications like traffic analysis, counting and classification of vehicles or pedestrians, event prediction, incident detection and security and surveillance systems. Those applications have to take into account some of the elements depicted in figure \ref{arch}, so developments in IMS have a wide range of approaches and objectives. In order to study IMS applications, five components have been defined in which applications have their main focus, although mutiple components could be involved in the same development. In figure  \ref{imsComps} a graph is presented, showing aforementioned components and elements within them.

@@

Application component could be seen as the final objective of the system. Generally, this includes high-level tasks like monitoring, analysis or control. Monitoring or surveillance systems execute actions like recognition, detection and/or tracking of objects in the scene. 
Other systems analyse the behaviour and interactions between detected objects to recognise path patterns, determine the context of the environment and predict some events of interest. In a higher level there are the control or decisions made based on detection of certain traffic conditions to handle traffic lights, generate warnings to drivers or issue traffic tickets when a rule violation exists.

>>>>

Intersection monitoring is a required task to be done within intelligent transportation systems for high-level applications like traffic analysis, counting and classification of vehicles or pedestrians, event prediction, incident detection and security and surveillance systems. Those applications have to take into account some of the elements depicted in figure \ref{arch} and developments in IMS have a wide range of approaches and objectives. In order to study IMS applications, five components have been defined, which are present on these applications, and on most cases, more than one component could be involved in the same development. In figure  \ref{imsComps} a graph is presented, showing aforementioned components and elements within them and then, a description of each component is given.

@@

Application component could be seen as the final objective of the system. Generally, this includes high-level tasks like monitoring, analysis or control. Monitoring or surveillance systems execute actions like recognition, detection and/or tracking of objects in the scene. 
Other systems analyse the behaviour and interactions between detected objects to recognise path patterns, determine the context of the environment and predict some events of interest. In \cite{Kamijo1999, Kamijo2000} is presented a system for accident detection and classification at intersections.In a higher level there are the control or decisions made based on detection of certain traffic conditions to handle traffic lights, control intersection access, generate warnings to drivers or issue traffic tickets when a rule violation exists.
